\documentclass[a4paper]{tufte-handout}

\usepackage[portuguese]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}

\newcommand{\workingDate}{\textsc{2024/2025}}
\newcommand{\userName}{João Sá Pereira}
\newcommand{\institution}{FEUP}

\usepackage{sample-handout}

%\title{An Example of the Usage of the Tufte-Handout Style\thanks{Inspired by Edward~R. Tufte!}}
%
%\author[The Tufte-LaTeX Developers]{The Tufte-\LaTeX\ Developers}
%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%
\title{Notas de Laboratório}
\subtitle{Bolsa de Investigação - INN4MIN}
\author[João Sá Pereira]{João Sá Pereira}
\date{2024/2025}
\publisher{Faculdade de Engenharia da Universidade do Porto}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\selectlanguage{portuguese}
    %%%%%%%%%%%%%%% TITLE %%%%%%%%%%%%%%%
	\maketitlepage
	\newpage
	\thispagestyle{empty}
	\topskip0pt
	\vspace*{\fill}
	\begin{projects}
		\begin{description}
			\item [INN4MIN] Desenvolvimento de metodologias inovadoras e sustentáveis aplicadas a recuperação de ouro e elementos críticos em minérios e placas de circuito integradas utilizadas\footnote{\href{https://cerena.pt/projects/inn4min-development-innovative-and-sustainable-approaches-applied-recovery-gold-and-1}{ERA-MIN3/0003/2021}}
		\end{description}
	\end{projects}

	\begin{planos}
		Lixiviação de uma amostra de ouro da mina do Numão (pré-concentrado, cerca de 15~kg)
		\begin{description}
			\item [Preparação de amostras:] Amostragens para sacos de 200/250~g.
			\item [Caracterização de amostras:] FRX, Digestão ABS, análise granulométrica $\rightarrow$ fazer em triplicado.
			\item [Lixiviação:] Plano de lixiviação com Tioreia (fazer exploratório e depois preparar plano de ensaios)
			\item [Lixiviação:] Plano de lixiviação com Citrato.
			\item [Lixiviação:] Plano de lixiviação com Bromo.
		\end{description}
		Fazer ensaios exploratórios com os 3 reagentes e, em função dos resultados, preparar plano mais exaustivo.
	\end{planos}

	% \begin{maybe}
	%     \begin{itemize}
	%     	\item Reimplement the ideas from the paper \textit{Getting Reference Counting Back in the Ring}
	%     \end{itemize}
	% \end{maybe}

	\vspace*{\fill}

	\newpage

	\pagestyle{fancy}

	%%%%%%%%%%%% Begining of document %%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{chapters/caracterizacao_amostras}


\begin{abstract}
\noindent
This document describes the Tufte handout \LaTeX\ document style.
It also provides examples and comments on the style's use.
Only a brief overview is presented here;
for a complete reference, see the sample book.
\end{abstract}

%\printclassoptions

The Tufte-\LaTeX\ document classes define a style similar to the
style Edward Tufte uses in his books and handouts.  Tufte's style is known
for its extensive use of sidenotes, tight integration of graphics with
text, and well-set typography.  This document aims to be at once a
demonstration of the features of the Tufte-\LaTeX\ document classes
and a style guide to their use.

% let's start a new thought -- a new section
\newthought{In his later books},\cite{fiuza_2011} Tufte
starts each section with a bit of vertical space, a non-indented paragraph,
and sets the first few words of the sentence in \textsc{small caps}.
 To accomplish this using this style, use the \Verb|\newthought| command:

\cleardoublepage
\pagestyle{plain}
\topskip0pt
\vspace*{\fill}
\bibliography{main}
\bibliographystyle{plainnat}
\vspace*{\fill}

\end{document}
